---
title: "STAT 413/613 Homework: Tidy Text"
author: "Jaehee Lee"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: no
    toc_depth: 4
    number_sections: yes
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align  = "center",
                      fig.height = 5, 
                      fig.width  = 6)
```

# Instructions {-}
1. Clone this homework repo to your homework directory as a new repo.
2. Rename the starter file under the analysis directory as `hw_01_yourname.Rmd` and use it for your solutions.   
3. Modify the "author" field in the YAML header.  
4. Stage and Commit R Markdown and HTML files (no PDF files).   
5. **Push both .Rmd and HTML files to GitHub**.   
- Make sure you have knitted to HTML prior to staging, committing, and pushing your final submission.  
6. **Commit each time you answer a part of question, e.g. 1.1**   
7. **Push to GitHub after each major question**   
8. When complete, submit a response in Canvas  

- Only include necessary code to answer the questions.
- Most of the functions you use should be from the tidyverse. 
- Unnecessary Base R or other packages not covered in class will result in point deductions.
- Use Pull requests and or email to ask me any questions. If you email, please ensure your most recent code is pushed to GitHub.


# Sentiment Analysis

Load library
```{r}
library(tidyverse)
library(tidytext)
library(stringr)
```

1. Download the following two works from the early 20^th^ century from Project Gutenberg:
- Upton Sinclair: "*The Jungle*" (1906)
- W.E.B. Du Bois: "*The Quest of the Silver Fleece*" (1911)
```{r}
library(gutenbergr)
# Upton Sinclair: "*The Jungle*" (1906)
gutenberg_works() %>%  
  filter(title == "The Jungle") %>%  
  select(gutenberg_id) -> jungle_id
gutenberg_download(jungle_id) -> jungle
# W.E.B. Du Bois: "*The Quest of the Silver Fleece*" (1911)
gutenberg_works() %>%  
  filter(title == "The Quest of the Silver Fleece: A Novel")  %>% 
  select(gutenberg_id) -> silver_id
gutenberg_download(silver_id) -> silver
```

