---
title: "STAT 413/613 Homework: Tidy Text"
author: "Jaehee Lee"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: no
    toc_depth: 4
    number_sections: yes
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align  = "center",
                      fig.height = 5, 
                      fig.width  = 6)
```

# Instructions {-}
1. Clone this homework repo to your homework directory as a new repo.
2. Rename the starter file under the analysis directory as `hw_01_yourname.Rmd` and use it for your solutions.   
3. Modify the "author" field in the YAML header.  
4. Stage and Commit R Markdown and HTML files (no PDF files).   
5. **Push both .Rmd and HTML files to GitHub**.   
- Make sure you have knitted to HTML prior to staging, committing, and pushing your final submission.  
6. **Commit each time you answer a part of question, e.g. 1.1**   
7. **Push to GitHub after each major question**   
8. When complete, submit a response in Canvas  

- Only include necessary code to answer the questions.
- Most of the functions you use should be from the tidyverse. 
- Unnecessary Base R or other packages not covered in class will result in point deductions.
- Use Pull requests and or email to ask me any questions. If you email, please ensure your most recent code is pushed to GitHub.


# Sentiment Analysis

Load library
```{r}
library(tidyverse)
library(tidytext)
library(stringr)
```

1. Download the following two works from the early 20^th^ century from Project Gutenberg:
- Upton Sinclair: "*The Jungle*" (1906)
- W.E.B. Du Bois: "*The Quest of the Silver Fleece*" (1911)
```{r}
library(gutenbergr)
```

```{r}
# Upton Sinclair: "*The Jungle*" (1906)
gutenberg_works() %>%  
  filter(title == "The Jungle") %>%  
  select(gutenberg_id) -> jungle_id
gutenberg_download(jungle_id) -> jungle
```

```{r}
# W.E.B. Du Bois: "*The Quest of the Silver Fleece*" (1911)
gutenberg_works() %>%  
  filter(title == "The Quest of the Silver Fleece: A Novel")  %>% 
  select(gutenberg_id) -> silver_id
gutenberg_download(silver_id) -> silver
```

2. Write a function 'to take an argument of a downloaded book tibble and return it in tidy text format.'
- The function must add line and chapter numbers as variables
- The function must unnest tokens at the word level
- The function must remove any Project Gutenberg formatting so only the words remain
- The function must remove any stop_words and filter out any `NA`s
- The function must remove any front matter (words before Chapter 1)
- The function can consider the unique nature of the front matter but cannot consider exactly how many chapters are in each book based on looking at the data i.e., no math based on knowing the number of chapters.
```{r}
jungle_function <- function(jungle){
  jungle %>%  
  mutate(linenumber = row_number()) %>%  
  mutate(chapter = cumsum(str_detect(text, regex("^CHAPTER [\\divxlc]",ignore_case = TRUE)))) %>%  
     ungroup() %>% 
  select(chapter, linenumber, everything()) -> jungle
  jungle <- jungle[-(1:51), , drop = FALSE]
  
  jungle%>% 
    unnest_tokens(word,text) %>%
    mutate(word = str_extract(word, "[a-z']+")) %>%
    anti_join(stop_words, by = "word") %>%  
  drop_na() -> jungle_jungle
  return(jungle_jungle)
}
# jungle_function(jungle)
```

```{r}
silver_function <- function(silver){
silver %>%  
  mutate(linenumber = row_number()) %>%  
  mutate(chapter = cumsum(str_detect(text, regex("(^_)([a-z]+)([-]{0,1})([a-z]+)(_$)",ignore_case = TRUE))))  %>%  
    ungroup() %>% 
  select(chapter, linenumber, everything())-> silver 
silver <- silver[-(1:143), , drop = FALSE]

silver %>%  
  unnest_tokens(word,text) %>% 
    mutate(word = str_extract(word, "[a-z']+")) %>% 
   anti_join(stop_words, by = "word") %>%  
  drop_na()  -> silver_silver
return(silver_silver)
}
# silver_function(silver)
```

3. Use the function from step 2
- Tidy each book and then add `book` and `author` as variables and save each tibble to a new variable. How many rows are in each book?
```{r}
jungle_function(jungle) %>%   
  mutate(author = "Upton Sinclair") %>%  
  mutate(book = "The Jungle") -> new_jungle
nrow(new_jungle)
```
```{r}
silver_function(silver) %>%  
 mutate(author = "W.E.B. Du Bois") %>%  
  mutate(book = "The Quest of the Silver Fleece: A Novel") -> new_silver
nrow(new_silver)
```

4. Use a dplyr function to combine the two tibbles into a new tibble. 
- It should have 89,434 rows with 6 variables
```{r}
bind_rows(mutate(new_jungle, author = "Upton Sinclair"), 
          mutate(new_silver, author = "W.E.B. Du Bois")) -> jungle_silver
nrow(jungle_silver)
```

5. Measure the net sentiment using bing for each block of 50 lines
- Plot the sentiment for each book in an appropriate faceted plot - either line or column. 
- Be sure to remove the legend.
- Save the plot to a variable
- Interpret the plots for each book and compare them.
```{r}
jungle_silver %>%  
  inner_join(get_sentiments("bing")) %>%  
  count(book, index = linenumber %/% 50, sentiment) %>%  
  spread(sentiment, n, fill = 0) %>%  
  mutate(sentiment = positive - negative) %>%  
  ggplot(aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x") -> compare_sentiment

compare_sentiment
```
Interpretation: Both of the books have significantly more negative sentiments compared to positive sentiments. This is because most of the lines are below 0. However, when we compare two graphs, it seems like "The Quest of the Silver Fleece" have more positive words than "the Jungle".

6. Measure the total for each nrc sentiment in each block of 500 lines and then,
- Filter out the "positive" and "negative" and save to a new variable. You should have 464 observations.
- Plot the count of the sentiments for each block in each book in an appropriate faceted plot with the books in two columns and the sentiments in 8 rows. 
- Be sure to remove the legend.
- Interpret the plots for each book and then compare them. 
- Why did the values drop off so suddenly at the end?
```{r}
get_sentiments("nrc") %>%  
  filter(sentiment != "positive" & sentiment != "negative") -> removed_data

jungle_silver %>%  
       inner_join(removed_data, by = "word") %>%  
      count(book, index = linenumber %/% 500, sentiment) -> observations
observations %>%  
  ggplot(aes(index, n, fill = sentiment)) + 
  geom_col(show.legend = FALSE) +
  facet_wrap(~book,scales = "free_y") 
```
7. Using bing, create a new data frame with the counts of the positive and negative sentiment words for each book.
- Show the "top 20" most frequent words across both books along with their book, sentiment, and count, in descending order by count.
- What are the positive words in the list of "top 20"?
```{r}
jungle_silver %>%  
  inner_join(get_sentiments("bing")) %>% 
  count(book, word, sentiment, sort = TRUE) -> bing_pos_neg

bing_pos_neg %>%  
    top_n(20) %>%  
    filter(sentiment == "positive") 
```

8. Plot the top ten for each positive and negative sentiment faceting by book.
- Ensure each facet has the words in the proper order for that book.
- Identify any that may be inappropriate for the context of the book and should be excluded from the sentiment analysis.
```{r}
bing_pos_neg %>% 
  group_by(sentiment, book) %>%  
  slice_max(order_by = n, n=10) %>%
  ungroup() %>%  
  mutate(word = reorder(word, n)) -> data 
data %>% 
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(sentiment~book, scales = "free_y") +
  labs(y = "Contribution to sentiment", x = NULL) +
  coord_flip()
```
I think removing word "miss" is better than removing other words. This is because the word miss has many different meanings that can be positive or negative or neutral. 
According to Cambridge dictionary, the word miss means several things:
1. to fail to do or experience something, often something planned or expected, or to avoid doing or experiencing something
2. to feel sad that a person or thing is not present
3. to fail to hit something, or to avoid hitting something
4. to notice that something is lost or absent
5. a girl or young woman, especially one who behaves rudely or shows no respect
6. a title used before the family name or full name of a single woman who has no other title 
and so on..
The word miss cannot always be negative. This is because miss can be used when calling someone such as "Miss Helena Lewis".


9. Remove the inappropriate word(s) from the analysis.
- Replot the top 10 for each sentiment per book from step 8.
- Interpret the plots
```{r}
data %>%  
  filter(word !=  "miss") %>% 
  group_by(sentiment, book) %>%  
  slice_max(order_by = n, n=10) %>%
  ungroup() %>%  
  mutate(word = reorder(word, n)) %>% 
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(sentiment~book, scales = "free_y") +
  labs(y = "Contribution to sentiment", x = NULL) +
  coord_flip()
```
Interpretation: 

The most frequently occurring word is "poor" in the negative words from the book "Jungle". “cold”, “lost” "wild",and “hard” are the next most frequently occurring words, which indicate that most people feel challenging about the life in the Jungle. 

The most frequently occurring word is "slowly" in the negative words from the book "The Quest of the Silver Fleece". "dark" is the next most frequently occurring words, which indicate that the background of this book is very dark and slow. 

The most frequently occurring word is "free" in the positive words from the book "Jungle". This indicates that people living in the Jungle have freedom. 

The most frequently occurring word is "love" in the positive words from the book "The Quest of the Silver Fleece". "mighty", "strong", "silent", "trust" are the next most frequently occuring words. This indicates that the characters in this book love each other with strong trust. 


10. Rerun the analysis from step 5 and recreate the plot with the title "Custom Bing".
- Show both the original step 5 plot with the new plot in the same output graphic, one on top of the other.
```{r}
get_sentiments("bing") %>%
  filter(word != "miss") ->
bing_no_miss

# Original
jungle_silver %>%  
  inner_join(get_sentiments("bing"), by = "word") %>%  
  count(book, index = linenumber %/% 50, sentiment) %>%  
  pivot_wider(names_from = sentiment, values_from = n, values_fill = list(n=0)) %>% 
  mutate(net = positive - negative) -> original
# Recreate 
jungle_silver %>%  
  inner_join(bing_no_miss, by = "word") %>%  
  count(book, index = linenumber %/% 50, sentiment) %>%  
  pivot_wider(names_from = sentiment, values_from = n, values_fill = list(n=0)) %>% 
  mutate(net = positive - negative) -> recreate

original %>%
  ggplot(aes(index, net, fill = book)) +
  geom_col(show.legend = FALSE) +
    ggtitle("Original") +
  facet_wrap(~book, ncol = 2, scales = "free_x") -> p1

recreate %>%
  ggplot(aes(index, net, fill = book)) +
  geom_col(show.legend = FALSE) + 
      ggtitle("Custom Bing") +
  facet_wrap(~book, ncol = 2, scales = "free_x") -> p2

library(gridExtra)
grid.arrange(p1, p2, nrow=2)
```
- Interpret the plots: 
For the Jungle plot,overall this book has more negative words than positive words ,however, there are some factors that make the characters positive feelings. What this implies is that maybe they encountered a lot of challenges while in Jungle, but while in the Jungle they feel other positive feelings.   

After removing the word miss, Custom bing plot of the book "The Quest of the Silver Fleece: A Novel" has more positive words compared to the original plot. This book also has negative feelings words a lot and based on that characters feel some kind of positive feelings. 

When we compare two books each other, we can say that the book Jungle is much more negative compared to the other one. This is because there are fewer lines above 0 in the Jungle plot than the other Sliver Fleece book plot. 
